### 2025-03-09 paper/preprint/paper.tex
okk

\usepackage{arxiv}
\usepackage{orcidlink}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage{placeins}
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{acacac}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\usepackage{amsthm}
\theoremstyle{plain}
\newtheorem{corollary}{Research Question}[section]
\theoremstyle{plain}
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\theoremstyle{remark}
\AtBeginDocument{\renewcommand*{\proofname}{Proof}}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\newtheorem{refremark}{Remark}[section]
\newtheorem{refsolution}{Solution}[section]
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\newcounter{quartocalloutnteno}
\newcommand{\quartocalloutnte}[1]{\refstepcounter{quartocalloutnteno}\label{#1}}

@@

\setcounter{section}{0}
\renewcommand{\thesection}{\Alph{section}}

\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}

\setcounter{figure}{0}
\renewcommand{\thefigure}{A\arabic{figure}}

@@

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, bottomrule=.15mm, coltitle=black, colback=white, titlerule=0mm, opacityback=0, rightrule=.15mm, bottomtitle=1mm, title={Note}, arc=.35mm, leftrule=.75mm, colbacktitle=quarto-callout-note-color!10!white, opacitybacktitle=0.6, colframe=quarto-callout-note-color-frame, breakable, toptitle=1mm, left=2mm]

@@

\subsubsection{Generator Parameters}\label{generator-parameters}

@@

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, bottomrule=.15mm, coltitle=black, colback=white, titlerule=0mm, opacityback=0, rightrule=.15mm, bottomtitle=1mm, title={Note \ref*{nte-gen-params-final-run-train}: Training Phase}, arc=.35mm, leftrule=.75mm, colbacktitle=quarto-callout-note-color!10!white, opacitybacktitle=0.6, colframe=quarto-callout-note-color-frame, breakable, toptitle=1mm, left=2mm]

@@

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, bottomrule=.15mm, coltitle=black, colback=white, titlerule=0mm, opacityback=0, rightrule=.15mm, bottomtitle=1mm, title={Note \ref*{nte-gen-params-final-run-eval}: Evaluation Phase}, arc=.35mm, leftrule=.75mm, colbacktitle=quarto-callout-note-color!10!white, opacitybacktitle=0.6, colframe=quarto-callout-note-color-frame, breakable, toptitle=1mm, left=2mm]

@@

@@

\subsubsection{Penalty Strengths}\label{penalty-strengths}

@@

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, bottomrule=.15mm, coltitle=black, colback=white, titlerule=0mm, opacityback=0, rightrule=.15mm, bottomtitle=1mm, title={Note \ref*{nte-pen-final-run-train}: Training Phase}, arc=.35mm, leftrule=.75mm, colbacktitle=quarto-callout-note-color!10!white, opacitybacktitle=0.6, colframe=quarto-callout-note-color-frame, breakable, toptitle=1mm, left=2mm]

@@

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, bottomrule=.15mm, coltitle=black, colback=white, titlerule=0mm, opacityback=0, rightrule=.15mm, bottomtitle=1mm, title={Note \ref*{nte-pen-final-run-eval}: Evaluation Phase}, arc=.35mm, leftrule=.75mm, colbacktitle=quarto-callout-note-color!10!white, opacitybacktitle=0.6, colframe=quarto-callout-note-color-frame, breakable, toptitle=1mm, left=2mm]

@@

@@

\subsubsection{Training Parameters}\label{training-parameters}

@@

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, bottomrule=.15mm, coltitle=black, colback=white, titlerule=0mm, opacityback=0, rightrule=.15mm, bottomtitle=1mm, title={Note \ref*{nte-train-final-run-train}: Training Phase}, arc=.35mm, leftrule=.75mm, colbacktitle=quarto-callout-note-color!10!white, opacitybacktitle=0.6, colframe=quarto-callout-note-color-frame, breakable, toptitle=1mm, left=2mm]

@@

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, bottomrule=.15mm, coltitle=black, colback=white, titlerule=0mm, opacityback=0, rightrule=.15mm, bottomtitle=1mm, title={Note \ref*{nte-train-final-run-eval}: Evaluation Phase}, arc=.35mm, leftrule=.75mm, colbacktitle=quarto-callout-note-color!10!white, opacitybacktitle=0.6, colframe=quarto-callout-note-color-frame, breakable, toptitle=1mm, left=2mm]

@@

>>>>

\usepackage{arxiv}
\usepackage{orcidlink}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage{placeins}
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{acacac}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\usepackage{amsthm}
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{plain}
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{plain}
\newtheorem{corollary}{Research Question}[section]
\theoremstyle{remark}
\AtBeginDocument{\renewcommand*{\proofname}{Proof}}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\newtheorem{refremark}{Remark}[section]
\newtheorem{refsolution}{Solution}[section]
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\newcounter{quartocalloutnteno}
\newcommand{\quartocalloutnte}[1]{\refstepcounter{quartocalloutnteno}\label{#1}}

@@

\renewcommand{\thesection}{\Alph{section}}

\renewcommand{\thetable}{A\arabic{table}}

\renewcommand{\thefigure}{A\arabic{figure}}

@@

\begin{tcolorbox}[enhanced jigsaw, colback=white, colframe=quarto-callout-note-color-frame, opacitybacktitle=0.6, toptitle=1mm, toprule=.15mm, leftrule=.75mm, rightrule=.15mm, coltitle=black, breakable, colbacktitle=quarto-callout-note-color!10!white, titlerule=0mm, left=2mm, arc=.35mm, opacityback=0, bottomtitle=1mm, bottomrule=.15mm, title={Note}]

@@

To assess the hyperparameter sensitivity of our proposed training regime
we ran multiple large grid searches for all of our synthetic datasets.
We have grouped these grid searches into multiple categories:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Generator Parameters} (Section~\ref{sec-app-grid-gen}):
  Investigates the effect of changing hyperparameters that affect the
  counterfactual outcomes during the training phase.
\item
  \textbf{Penalty Strengths} (Section~\ref{sec-app-grid-pen}):
  Investigates the effect of changing the penalty strengths in out
  proposed objective (Equation~\ref{eq-obj}).
\item
  \textbf{Other Parameters} (Section~\ref{sec-app-grid-train}):
  Investigates the effect of changing other training parameters,
  including the total number of generated counterfactuals in each epoch.
\end{enumerate}

We begin by summarizing the high-level findings in
Section~\ref{sec-app-grid-hl}. For each of the categories,
Section~\ref{sec-app-grid-gen} to Section~\ref{sec-app-grid-train} then
present all details including the parameter grids, average performance
outcomes and key evaluation metrics for the generated counterfactuals.

\subsubsection{High-Level Findings}\label{sec-app-grid-hl}

Overall, we find that Counterfactual Training (CT) achieves it key
objectives consistently across all hyperparameter settings and also
broadly across datasets. We do observe strong sensitivity to certain
hyperparameters, but clear and manageable patterns emerge in those
cases. With respect to the underlying training data distribution, we
find that outcomes for CT seem to depend to some degree on class
separability.

\paragraph{Predictive Performance}\label{predictive-performance}

We find that CT is associated with little to no decrease in average
predictive performance for our synthetic datasets: test accuracy and
F1-scores decrease by at most \textasciitilde1 percentage point, but
generally much less (Table~\ref{tbl-acc-gen}, Table~\ref{tbl-acc-pen},
Table~\ref{tbl-acc-train}).

\paragraph{Key Counterfactual
Outcomes}\label{key-counterfactual-outcomes}

\subsubsection{Generator Parameters}\label{sec-app-grid-gen}

@@

\begin{tcolorbox}[enhanced jigsaw, colback=white, colframe=quarto-callout-note-color-frame, opacitybacktitle=0.6, toptitle=1mm, toprule=.15mm, leftrule=.75mm, rightrule=.15mm, coltitle=black, breakable, colbacktitle=quarto-callout-note-color!10!white, titlerule=0mm, left=2mm, arc=.35mm, opacityback=0, bottomtitle=1mm, bottomrule=.15mm, title={Note \ref*{nte-gen-params-final-run-train}: Training Phase}]

@@

\begin{tcolorbox}[enhanced jigsaw, colback=white, colframe=quarto-callout-note-color-frame, opacitybacktitle=0.6, toptitle=1mm, toprule=.15mm, leftrule=.75mm, rightrule=.15mm, coltitle=black, breakable, colbacktitle=quarto-callout-note-color!10!white, titlerule=0mm, left=2mm, arc=.35mm, opacityback=0, bottomtitle=1mm, bottomrule=.15mm, title={Note \ref*{nte-gen-params-final-run-eval}: Evaluation Phase}]

@@

\paragraph{Accuracy}\label{accuracy}

\begin{longtable}{ccccc}

\caption{\label{tbl-acc-gen}Predictive performance measures by dataset
and objective averaged across training-phase parameters
(Note~\ref{nte-gen-params-final-run-train}) and evaluation-phase
parameters (Note~\ref{nte-gen-params-final-run-eval}).}

\tabularnewline

  \toprule
  \textbf{Dataset} & \textbf{Variable} & \textbf{Objective} & \textbf{Mean} & \textbf{Std} \\\midrule
  \endfirsthead
  \toprule
  \textbf{Dataset} & \textbf{Variable} & \textbf{Objective} & \textbf{Mean} & \textbf{Std} \\\midrule
  \endhead
  \bottomrule
  \multicolumn{5}{r}{Continuing table below.}\\
  \bottomrule
  \endfoot
  \endlastfoot
  Circles & Accuracy & Full & 0.997 & 0.00309 \\
  Circles & Accuracy & Vanilla & 0.998 & 0.000557 \\
  Circles & F1-score & Full & 0.997 & 0.00309 \\
  Circles & F1-score & Vanilla & 0.998 & 0.000558 \\
  Lin Sep & Accuracy & Full & 0.999 & 0.00201 \\
  Lin Sep & Accuracy & Vanilla & 1 & 0 \\
  Lin Sep & F1-score & Full & 0.999 & 0.00201 \\
  Lin Sep & F1-score & Vanilla & 1 & 0 \\
  Moons & Accuracy & Full & 0.999 & 0.000696 \\
  Moons & Accuracy & Vanilla & 1 & 0.00111 \\
  Moons & F1-score & Full & 0.999 & 0.000696 \\
  Moons & F1-score & Vanilla & 1 & 0.00111 \\
  Over & Accuracy & Full & 0.915 & 0.00477 \\
  Over & Accuracy & Vanilla & 0.917 & 0.00123 \\
  Over & F1-score & Full & 0.915 & 0.00478 \\
  Over & F1-score & Vanilla & 0.917 & 0.00124 \\\bottomrule

\end{longtable}

@@

\subsubsection{Penalty Strengths}\label{sec-app-grid-pen}

@@

\begin{tcolorbox}[enhanced jigsaw, colback=white, colframe=quarto-callout-note-color-frame, opacitybacktitle=0.6, toptitle=1mm, toprule=.15mm, leftrule=.75mm, rightrule=.15mm, coltitle=black, breakable, colbacktitle=quarto-callout-note-color!10!white, titlerule=0mm, left=2mm, arc=.35mm, opacityback=0, bottomtitle=1mm, bottomrule=.15mm, title={Note \ref*{nte-pen-final-run-train}: Training Phase}]

@@

\begin{tcolorbox}[enhanced jigsaw, colback=white, colframe=quarto-callout-note-color-frame, opacitybacktitle=0.6, toptitle=1mm, toprule=.15mm, leftrule=.75mm, rightrule=.15mm, coltitle=black, breakable, colbacktitle=quarto-callout-note-color!10!white, titlerule=0mm, left=2mm, arc=.35mm, opacityback=0, bottomtitle=1mm, bottomrule=.15mm, title={Note \ref*{nte-pen-final-run-eval}: Evaluation Phase}]

@@

\paragraph{Accuracy}\label{accuracy-1}

\begin{longtable}{ccccc}

\caption{\label{tbl-acc-pen}Predictive performance measures by dataset
and objective averaged across training-phase parameters
(Note~\ref{nte-pen-final-run-train}) and evaluation-phase parameters
(Note~\ref{nte-pen-final-run-eval}).}

\tabularnewline

  \toprule
  \textbf{Dataset} & \textbf{Variable} & \textbf{Objective} & \textbf{Mean} & \textbf{Std} \\\midrule
  \endfirsthead
  \toprule
  \textbf{Dataset} & \textbf{Variable} & \textbf{Objective} & \textbf{Mean} & \textbf{Std} \\\midrule
  \endhead
  \bottomrule
  \multicolumn{5}{r}{Continuing table below.}\\
  \bottomrule
  \endfoot
  \endlastfoot
  Circles & Accuracy & Full & 0.994 & 0.0144 \\
  Circles & Accuracy & Vanilla & 0.998 & 0.000875 \\
  Circles & F1-score & Full & 0.994 & 0.0145 \\
  Circles & F1-score & Vanilla & 0.998 & 0.000875 \\
  Lin Sep & Accuracy & Full & 0.998 & 0.00772 \\
  Lin Sep & Accuracy & Vanilla & 1 & 0 \\
  Lin Sep & F1-score & Full & 0.998 & 0.00773 \\
  Lin Sep & F1-score & Vanilla & 1 & 0 \\
  Moons & Accuracy & Full & 0.987 & 0.0351 \\
  Moons & Accuracy & Vanilla & 0.998 & 0.0101 \\
  Moons & F1-score & Full & 0.987 & 0.0352 \\
  Moons & F1-score & Vanilla & 0.998 & 0.0102 \\
  Over & Accuracy & Full & 0.911 & 0.0217 \\
  Over & Accuracy & Vanilla & 0.916 & 0.00236 \\
  Over & F1-score & Full & 0.911 & 0.0219 \\
  Over & F1-score & Vanilla & 0.916 & 0.00236 \\\bottomrule

\end{longtable}

@@

\subsubsection{Other Parameters}\label{sec-app-grid-train}

@@

\begin{tcolorbox}[enhanced jigsaw, colback=white, colframe=quarto-callout-note-color-frame, opacitybacktitle=0.6, toptitle=1mm, toprule=.15mm, leftrule=.75mm, rightrule=.15mm, coltitle=black, breakable, colbacktitle=quarto-callout-note-color!10!white, titlerule=0mm, left=2mm, arc=.35mm, opacityback=0, bottomtitle=1mm, bottomrule=.15mm, title={Note \ref*{nte-train-final-run-train}: Training Phase}]

@@

\begin{tcolorbox}[enhanced jigsaw, colback=white, colframe=quarto-callout-note-color-frame, opacitybacktitle=0.6, toptitle=1mm, toprule=.15mm, leftrule=.75mm, rightrule=.15mm, coltitle=black, breakable, colbacktitle=quarto-callout-note-color!10!white, titlerule=0mm, left=2mm, arc=.35mm, opacityback=0, bottomtitle=1mm, bottomrule=.15mm, title={Note \ref*{nte-train-final-run-eval}: Evaluation Phase}]

@@

\paragraph{Accuracy}\label{accuracy-2}

\begin{longtable}{ccccc}

\caption{\label{tbl-acc-train}Predictive performance measures by dataset
and objective averaged across training-phase parameters
(Note~\ref{nte-train-final-run-train}) and evaluation-phase parameters
(Note~\ref{nte-train-final-run-eval}).}

\tabularnewline

  \toprule
  \textbf{Dataset} & \textbf{Variable} & \textbf{Objective} & \textbf{Mean} & \textbf{Std} \\\midrule
  \endfirsthead
  \toprule
  \textbf{Dataset} & \textbf{Variable} & \textbf{Objective} & \textbf{Mean} & \textbf{Std} \\\midrule
  \endhead
  \bottomrule
  \multicolumn{5}{r}{Continuing table below.}\\
  \bottomrule
  \endfoot
  \endlastfoot
  Circles & Accuracy & Full & 0.995 & 0.00431 \\
  Circles & Accuracy & Vanilla & 0.998 & 0.000566 \\
  Circles & F1-score & Full & 0.995 & 0.00432 \\
  Circles & F1-score & Vanilla & 0.998 & 0.000566 \\
  Lin Sep & Accuracy & Full & 0.999 & 0.00231 \\
  Lin Sep & Accuracy & Vanilla & 1 & 0 \\
  Lin Sep & F1-score & Full & 0.999 & 0.00231 \\
  Lin Sep & F1-score & Vanilla & 1 & 0 \\
  Moons & Accuracy & Full & 0.996 & 0.0136 \\
  Moons & Accuracy & Vanilla & 0.988 & 0.022 \\
  Moons & F1-score & Full & 0.996 & 0.0136 \\
  Moons & F1-score & Vanilla & 0.988 & 0.022 \\
  Over & Accuracy & Full & 0.914 & 0.00563 \\
  Over & Accuracy & Vanilla & 0.918 & 0.00116 \\
  Over & F1-score & Full & 0.914 & 0.0057 \\
  Over & F1-score & Vanilla & 0.918 & 0.00116 \\\bottomrule

\end{longtable}

### 2025-03-09 paper/sections/other/grids.qmd
okk

### Generator Parameters

```{julia}
grid_dir = joinpath(res_dir, "gen_params/mlp")
data_dirs = readdir(grid_dir) |> x -> joinpath.(grid_dir, x) |> x -> x[isdir.(x)]
data_names = basename.(data_dirs)
suffix = "evaluation/results/ce/decision_threshold_exper---lambda_energy_exper---maxiter_exper---maxiter---decision_threshold_exper/"
```

@@

@@

### Penalty Strengths

```{julia}
grid_dir = joinpath(res_dir, "penalties/mlp")
data_dirs = readdir(grid_dir) |> x -> joinpath.(grid_dir, x) |> x -> x[isdir.(x)]
data_names = basename.(data_dirs)
suffix = "evaluation/results/ce/lambda_adversarial---lambda_energy_reg---lambda_energy_diff---lambda_adversarial---lambda_adversarial/"
```

@@

@@

### Training Parameters

```{julia}
grid_dir = joinpath(res_dir, "training_params/mlp")
data_dirs = readdir(grid_dir) |> x -> joinpath.(grid_dir, x) |> x -> x[isdir.(x)]
data_names = basename.(data_dirs)
suffix = "evaluation/results/ce/burnin---nce---nepochs---burnin---burnin/"
```

@@

>>>>

To assess the hyperparameter sensitivity of our proposed training regime we ran multiple large grid searches for all of our synthetic datasets. We have grouped these grid searches into multiple categories:

1. **Generator Parameters** (@sec-app-grid-gen): Investigates the effect of changing hyperparameters that affect the counterfactual outcomes during the training phase.
2. **Penalty Strengths** (@sec-app-grid-pen): Investigates the effect of changing the penalty strengths in out proposed objective (@eq-obj).
3. **Other Parameters** (@sec-app-grid-train): Investigates the effect of changing other training parameters, including the total number of generated counterfactuals in each epoch.

We begin by summarizing the high-level findings in @sec-app-grid-hl. For each of the categories, @sec-app-grid-gen to @sec-app-grid-train then present all details including the parameter grids, average performance outcomes and key evaluation metrics for the generated counterfactuals.

### High-Level Findings {#sec-app-grid-hl}

Overall, we find that Counterfactual Training (CT) achieves it key objectives consistently across all hyperparameter settings and also broadly across datasets. We do observe strong sensitivity to certain hyperparameters, but clear and manageable patterns emerge in those cases. With respect to the underlying training data distribution, we find that outcomes for CT seem to depend to some degree on class separability.

#### Predictive Performance

We find that CT is associated with little to no decrease in average predictive performance for our synthetic datasets: test accuracy and F1-scores decrease by at most ~1 percentage point, but generally much less (@tbl-acc-gen, @tbl-acc-pen, @tbl-acc-train).

#### Key Counterfactual Outcomes

### Generator Parameters {#sec-app-grid-gen}

```{julia}
grid_dir = joinpath(res_dir, "gen_params/mlp")
data_dirs = readdir(grid_dir) |> x -> joinpath.(grid_dir, x) |> x -> x[isdir.(x)]
eval_grids = (p -> EvaluationGrid(joinpath(p,"grid_config.toml"))).(data_dirs)
data_names = basename.(data_dirs)
suffix = "evaluation/results/ce/decision_threshold_exper---lambda_energy_exper---maxiter_exper---maxiter---decision_threshold_exper/"
```

@@

#### Accuracy

::: {#tbl-acc-gen}

::: {.content-hidden unless-format="pdf"}

```{julia}
#| output: asis
df = CTExperiments.aggregate_performance(eval_grids; byvars=["objective"]) 
get_table_inputs(df, "mean";backend=Val(:latex)) |>
    inputs -> tabulate_results(inputs; wrap_table=false)
```

Predictive performance measures by dataset and objective averaged across training-phase parameters (@nte-gen-params-final-run-train) and evaluation-phase parameters (@nte-gen-params-final-run-eval).

@@

### Penalty Strengths {#sec-app-grid-pen}

```{julia}
grid_dir = joinpath(res_dir, "penalties/mlp")
data_dirs = readdir(grid_dir) |> x -> joinpath.(grid_dir, x) |> x -> x[isdir.(x)]
eval_grids = (p -> EvaluationGrid(joinpath(p,"grid_config.toml"))).(data_dirs)
data_names = basename.(data_dirs)
suffix = "evaluation/results/ce/lambda_adversarial---lambda_energy_reg---lambda_energy_diff---lambda_adversarial---lambda_adversarial/"
```

@@

#### Accuracy

::: {#tbl-acc-pen}

::: {.content-hidden unless-format="pdf"}

```{julia}
#| output: asis
df = CTExperiments.aggregate_performance(eval_grids; byvars=["objective"]) 
get_table_inputs(df, "mean";backend=Val(:latex)) |>
    inputs -> tabulate_results(inputs; wrap_table=false)
```

Predictive performance measures by dataset and objective averaged across training-phase parameters (@nte-pen-final-run-train) and evaluation-phase parameters (@nte-pen-final-run-eval).

@@

### Other Parameters {#sec-app-grid-train}

```{julia}
grid_dir = joinpath(res_dir, "training_params/mlp")
data_dirs = readdir(grid_dir) |> x -> joinpath.(grid_dir, x) |> x -> x[isdir.(x)]
eval_grids = (p -> EvaluationGrid(joinpath(p,"grid_config.toml"))).(data_dirs)
data_names = basename.(data_dirs)
suffix = "evaluation/results/ce/burnin---nce---nepochs---burnin---burnin/"
```

@@

#### Accuracy

::: {#tbl-acc-train}

::: {.content-hidden unless-format="pdf"}

```{julia}
#| output: asis
df = CTExperiments.aggregate_performance(eval_grids; byvars=["objective"]) 
get_table_inputs(df, "mean";backend=Val(:latex)) |>
    inputs -> tabulate_results(inputs; wrap_table=false)
```

Predictive performance measures by dataset and objective averaged across training-phase parameters (@nte-train-final-run-train) and evaluation-phase parameters (@nte-train-final-run-eval).
